---
title: "Chapter 7 Time Series Regression Models"
author: "AG"
date: "19/01/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggfortify)
library(fpp3)
library(fpp2)
library(tsibble)
library(fma)
library(imputeTS)
knitr::opts_chunk$set(echo = TRUE)
```

## The Linear Model
### Linear Regression

```{r}
us_change

us_change %>%
  pivot_longer(c(Consumption, Income), names_to = "Series")

us_change %>%
  pivot_longer(c(Consumption, Income), names_to = "Series") %>%
  autoplot(value) +
  labs(y = "% change")


us_change %>% pivot_longer(c(Consumption, Income), names_to = "Series") %>% ggplot(aes(x = Quarter, y = value)) + geom_line() + facet_grid(vars(Series))
```

```{r}
us_change %>%
  ggplot(aes(x = Income, y = Consumption)) +
  labs(y = "Consumption (quarterly % change)", x = "Income (quarterly % change)") +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```
```{r}
us_change %>%
  model(TSLM(Consumption ~ Income)) %>%
  report()
```

```{r}
us_change %>%
  GGally::ggpairs(columns = 2:6)
```

## Least Square Estimation

```{r}
fit.consMR <- us_change %>%
  model(tslm = TSLM(Consumption ~ Income + Production + Unemployment + Savings))
report(fit.consMR)
```

###Fitted Values
```{r}
augment(fit.consMR) %>%
  ggplot(aes(x = Quarter)) +
  geom_line(aes(y = Consumption, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted")) +
  labs(y = NULL, title = "Percent change in US consumption expenditure") +
  scale_color_manual(values=c(Data="black",Fitted="red")) +
  guides(colour = guide_legend(title = NULL))
```


```{r}
augment(fit.consMR) %>%
  ggplot(aes(x = Consumption, y = .fitted)) +
  geom_point() +
  labs(y = "Fitted (predicted values)",
       x = "Data (actual values)",
       title = "Percent change in US consumption expenditure") +
  geom_abline(intercept = 0, slope = 1)
```

## Evaluating the regression model


### Plotting Residuals
```{r}
fit.consMR %>% gg_tsresiduals()
```

```{r}
augment(fit.consMR) %>% features(.innov, ljung_box, lag = 10, dof = 5)
```
### Residual plots against predictors
```{r}
df <- left_join(us_change, residuals(fit.consMR), by = "Quarter")
p1 <- ggplot(df, aes(x = Income, y = .resid)) +
  geom_point() + labs(y = "Residuals")
p2 <- ggplot(df, aes(x = Production, y = .resid)) +
  geom_point() + labs(y = "Residuals")
p3 <- ggplot(df, aes(x = Savings, y = .resid)) +
  geom_point() + labs(y = "Residuals")
p4 <- ggplot(df, aes(x = Unemployment, y = .resid)) +
  geom_point() + labs(y = "Residuals")
p1
p2
p3
p4
```

### Residual plots against fitted values

```{r}
augment(fit.consMR) %>%
  ggplot(aes(x = .fitted, y = .resid)) +
  geom_point() + labs(x = "Fitted", y = "Residuals")
```
## Spurious Regression

```{r}
fit <- aus_airpassengers %>%
  filter(Year <= 2011) %>%
  left_join(guinea_rice, by = "Year") %>%
  model(TSLM(Passengers ~ Production))
report(fit)

fit %>% gg_tsresiduals()
```
## Some Userful Predictions
### Trend, Dummy Variable, Seasonal Dummy Variable

```{r}
recent_production <- aus_production %>%
  filter(year(Quarter) >= 1992)
recent_production %>%
  autoplot(Beer) +
  labs(y = "Megalitres")
```

```{r}
fit_beer <- recent_production %>%
  model(TSLM(Beer ~ trend() + season()))
report(fit_beer)
```
```{r}
augment(fit_beer) %>%
  ggplot(aes(x = Quarter)) +
  geom_line(aes(y = Beer, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted")) +
  scale_color_manual(values = c(Data = "black", Fitted = "red")) +
  labs(y = "Megalitres", title = "Quarterly Beer Production") +
  guides(colour = guide_legend(title = "Series"))
```

```{r}
augment(fit_beer) %>%
  ggplot(aes(x = Beer, y = .fitted, colour = factor(quarter(Quarter)))) +
  geom_point() +
  labs(y = "Fitted", x = "Actual values",
       title = "Quarterly beer production") +
  geom_abline(intercept = 0, slope = 1) +
  guides(colour = guide_legend(title = "Quarter"))
```
### Fourier Transform
```{r}
fourier_beer <- recent_production %>%
  model(TSLM(Beer ~ trend() + fourier(K = 2)))
report(fourier_beer)
```
## Selecting predictors

```{r}
glance(fit.consMR) %>% select(adj_r_squared, CV, AIC, AICc, BIC)
```

## Forecasting with regression
### Ex-ante vs Ex-posts forecast
```{r}
recent_production <- aus_production %>% filter(year(Quarter) >= 1992)
fit_beer <- recent_production %>%
  model(TSLM(Beer ~ trend() + season()))
fc_beer <- forecast(fit_beer)
fc_beer %>%
  autoplot(recent_production) +
  labs(title = "Forecasts of beer production using regression",
       y = "megalitres")
```

### Scenario-based forecast
```{r}
fit_consBest <- us_change %>%
  model(lm = TSLM(Consumption ~ Income + Savings + Unemployment))

future_scenarios <- scenarios(
  Increase = new_data(us_change, 4) %>% mutate(Income=1, Savings=0.5, Unemployment=0),
  Decrease = new_data(us_change, 4) %>% mutate(Income=-1, Savings=-0.5, Unemployment=0),
  names_to = "Scenario")

fc <- forecast(fit_consBest, new_data = future_scenarios)
```


```{r}
us_change %>%
  autoplot(Consumption) +
  autolayer(fc) +
  labs(y = "% change in US consumption")
```
### Prediction Intervals

```{r}
fit_cons <- us_change %>%
  model(TSLM(Consumption ~ Income))
new_cons <- scenarios(
  "Average increase" = new_data(us_change, 4) %>% mutate(Income = mean(us_change$Income)),
  "Extreme increase" = new_data(us_change, 4) %>% mutate(Income = 12),
  names_to = "Scenario"
)
fcast <- forecast(fit_cons, new_cons)

us_change %>%
  autoplot(Consumption) +
  autolayer(fcast) +
  labs(y = "% change in US consumption")
```

## Nonlinear Regression

```{r}
boston_men <- boston_marathon %>%
  filter(Year >= 1924) %>%
  filter(Event == "Men's open division") %>%
  mutate(Minutes = as.numeric(Time)/60)

boston_men
```
```{r}
fit_boston_men <- boston_men %>%
  model(TSLM(Minutes ~ trend()))
report(fit_boston_men)
```

```{r}
augment(fit_boston_men) %>%
  ggplot(aes(x = Year)) +
  geom_line(aes(y = Minutes, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted")) +
  scale_color_manual(values = c(Data = "black", Fitted = "red"))

fit_boston_men %>% gg_tsresiduals()
```

```{r}
fit_trends <- boston_men %>%
  model(
    linear = TSLM(Minutes ~ trend()),
    exponential = TSLM(log(Minutes) ~ trend()),
    piecewise = TSLM(Minutes ~ trend(knots = c(1950, 1980)))
  )
fc_trends <- fit_trends %>% forecast(h = 10)

boston_men %>%
  autoplot(Minutes) +
  geom_line(aes(y = .fitted, colour = .model), data = fitted(fit_trends)) +
  autolayer(fc_trends, alpha = 0.5, level = 95) +
  labs(y = "Winning times in minutes",
       title = "Boston Marathon")
```

## Exercise

### Question 1

```{r}
jan14_vic_elec <- vic_elec %>%
  filter(yearmonth(Time) == yearmonth("2014 Jan")) %>%
  index_by(Date = as_date(Time)) %>%
  summarise(Demand = sum(Demand), Temperature = max(Temperature))

jan14_vic_elec

jan14_vic_elec %>% pivot_longer(c(Demand, Temperature), names_to = "Series") %>% ggplot(aes(x = Date, y = value)) + geom_line() + facet_grid(vars(Series), scales = "free")

jan14_vic_elec %>% GGally::ggpairs(columns = 2:3)

jan14_vic_elec %>%
  ggplot(aes(x = Temperature, y = Demand)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)


jan14_vic_elec %>%
  model(TSLM(Demand ~ Temperature)) %>%
  report()

fit.consMR <- jan14_vic_elec %>%
  model(tslm = TSLM(Demand ~ Temperature))
report(fit.consMR)

augment(fit.consMR) %>%
  ggplot(aes(x = Date)) +
  geom_line(aes(y = Demand, colour = "Data")) +
  geom_line(aes(y = .fitted, colour = "Fitted")) +
  scale_color_manual(values=c(Data="black",Fitted="red")) +
  guides(colour = guide_legend(title = NULL))


augment(fit.consMR) %>%
  ggplot(aes(x = Demand, y = .fitted)) +
  geom_point() +
  labs(y = "Fitted (predicted values)",
       x = "Data (actual values)") +
  geom_abline(intercept = 0, slope = 1)


fit.consMR %>% gg_tsresiduals()

augment(fit.consMR) %>% features(.innov, ljung_box, lag = 10, dof = 5)


df <- left_join(jan14_vic_elec, residuals(fit.consMR), by = "Date")
p1 <- ggplot(df, aes(x = Temperature, y = .resid)) +
  geom_point() + labs(y = "Residuals")

p1

jan14_vic_elec %>%
  model(TSLM(Demand ~ Temperature)) %>%
  forecast(
    new_data(jan14_vic_elec, 1) %>% mutate(Temperature = 15)
  ) %>%
  autoplot(jan14_vic_elec)

new_model <- jan14_vic_elec %>% model(TSLM(Demand ~ Temperature))

future_scenarios <- scenarios(
  Increase = new_data(jan14_vic_elec, 1) %>% mutate(Temperature = 35),
  Decrease = new_data(jan14_vic_elec, 1) %>% mutate(Temperature = 15),
  names_to = "Scenario")

future_scenarios

fc <- forecast(new_model, new_data = future_scenarios)

jan14_vic_elec %>%
  autoplot(Demand) +
  autolayer(fc)


vic_elec %>% ggplot(aes(x = Temperature, y = Demand)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)
```
### Question 2
```{r}
olympic_running

olympic_running %>% mutate(Length = as.factor(Length)) %>% ggplot(aes(x=Year, y=Time)) + facet_grid(rows=vars(Length),cols=vars(Sex), scales= "free") + geom_line() + geom_point()


olympic_running %>% filter(Year >= 1950, Length == 100, Sex== "men") %>% autoplot(Time)

fit_olympic_running <- olympic_running %>% filter(Year >= 1950, Length == 100, Sex== "men") %>% select(Time) %>% model(tslm = TSLM(Time ~ Year))

report(fit_olympic_running)



```




























































