---
title: "Chapter 5 Forecaster's Toolbox"
author: "Abhishek Gupta"
date: "15/09/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggfortify)
library(fpp3)
library(fpp2)
library(tsibble)
library(fma)
library(imputeTS)
knitr::opts_chunk$set(echo = TRUE)
```
# A Tidy workflow

## Visualizing Time Series

```{r}
global_economy %>%
  filter(Country=="Sweden") %>%
  autoplot(GDP) +
    ggtitle("GDP for Sweden") + ylab("$US billions")
```
## Define the model

```{r}
TSLM(GDP ~ trend())
```

## Train the model

```{r}
fit <- global_economy %>%
  model(trend_model = TSLM(GDP ~ trend()))
```
```{r}
fit
```
## Evaluate

## Forecast

```{r}
fit %>% forecast(h = "3 years")
```
```{r}
fit %>% forecast(h = "3 years") %>%
  filter(Country=="Sweden") %>%
  autoplot(global_economy) +
    ggtitle("GDP for Sweden") + ylab("$US billions")
```
# Some simple forecasting methods

```{r}
bricks <- aus_production %>% filter(between(year(Quarter), 1970, 2004))
bricks
```

## Average Method

```{r}
fit <- bricks %>% model(MEAN(Bricks))
fit %>% forecast(h = "5 years") %>%
  autoplot(bricks)
```
## Naive Method

```{r}
bricks %>% model(NAIVE(Bricks)) %>% forecast(h ="5 years") %>% autoplot(bricks)
```
## Seasonal Naive Method

```{r}
bricks %>% model(SNAIVE(Bricks ~ lag("year"))) %>% forecast(h="5 years") %>%autoplot(bricks)
```

## Drift Method

```{r}
bricks %>% model(RW(Bricks ~ drift())) %>% forecast(h='10 years')%>% autoplot(bricks)
```
## Example 1
```{r}
# Set training data from 1992 to 2006
train <- aus_production %>% filter_index("1992 Q1" ~ "2006 Q4")
# Fit the models
beer_fit <- train %>%
  model(
    Mean = MEAN(Beer),
    `Naïve` = NAIVE(Beer),
    `Seasonal naïve` = SNAIVE(Beer)
  )
# Generate forecasts for 14 quarters
beer_fc <- beer_fit %>% forecast(h=14)
# Plot forecasts against actual values
beer_fc %>%
  autoplot(train, level = NULL) +
    autolayer(filter_index(aus_production, "2007 Q1" ~ .), color = "black") +
    ggtitle("Forecasts for quarterly beer production") +
    xlab("Year") + ylab("Megalitres") +
    guides(colour=guide_legend(title="Forecast"))
```
## Example 2

```{r}
# Re-index based on trading days
google_stock <- gafa_stock %>%
  filter(Symbol == "GOOG") %>%
  mutate(day = row_number()) %>%
  update_tsibble(index = day, regular = TRUE)
# Filter the year of interest
google_2015 <- google_stock %>% filter(year(Date) == 2015)
# Fit the models
google_fit <- google_2015 %>%
  model(
    Mean = MEAN(Close),
    `Naïve` = NAIVE(Close),
    Drift = NAIVE(Close ~ drift())
  )
# Produce forecasts for the 19 trading days in January 2015
google_fc <- google_fit %>% forecast(h = 19)
# A better way using a tsibble to determine the forecast horizons
google_jan_2016 <- google_stock %>%
  filter(yearmonth(Date) == yearmonth("2016 Jan"))
google_fc <- google_fit %>% forecast(google_jan_2016)
# Plot the forecasts
google_fc %>%
  autoplot(google_2015, level = NULL) +
    autolayer(google_jan_2016, Close, color='black') +
    ggtitle("Google stock (daily ending 31 Dec 2015)") +
    xlab("Day") + ylab("Closing Price (US$)") +
    guides(colour=guide_legend(title="Forecast"))
```
# Fitted values and Residuals

## Residuals

```{r}
augment(beer_fit)
```

# Residual Diagnostics

```{r}
google_2015 %>% autoplot(Close) +
  xlab("Day") + ylab("Closing Price (US$)") +
  ggtitle("Google Stock in 2015")
```

```{r}
aug <- google_2015 %>% model(NAIVE(Close)) %>% augment()
aug %>% autoplot(.resid) + xlab("Day") + ylab("") +
  ggtitle("Residuals from naïve method")
```
```{r}
aug %>%
  ggplot(aes(x = .resid)) +
  geom_histogram() +
  ggtitle("Histogram of residuals")
```
```{r}
aug %>% ACF(.resid) %>% autoplot() + ggtitle("ACF of residuals")
```
```{r}
google_2015 %>% model(NAIVE(Close)) %>% gg_tsresiduals()
```
## Portmanteau tests for autocorrelation 

```{r}
# lag=h and fitdf=K
aug %>% features(.resid, box_pierce, lag=10, dof=0)
```


```{r}
aug %>% features(.resid, ljung_box, lag=10, dof=0)
```

```{r}
fit <- google_2015 %>% model(RW(Close~drift()))
fit %>% tidy()
```

```{r}
augment(fit) %>% features(.resid, ljung_box, lag=10, dof=1)
```

# Distributional Forecasts and Prediction Intervals

## Multistep prediction interval: Benchmark methods

```{r}
google_2015 %>%
  model(NAIVE(Close)) %>%
  forecast(h = 10) %>%
  hilo()
```
## Prediction intervals from bootstrapped residuals

```{r}
fit <- google_2015 %>%
  model(NAIVE(Close))
sim <- fit %>% generate(h = 30, times = 5, bootstrap = TRUE)
sim
```

```{r}
google_2015 %>%
  ggplot(aes(x = day)) +
  geom_line(aes(y = Close)) +
  geom_line(aes(y = .sim, colour = as.factor(.rep)), data = sim) +
  ggtitle("Google closing stock price") +
  guides(col = FALSE)
```
```{r}
fc <- fit %>% forecast(h = 30, bootstrap = TRUE)
fc
```
```{r}
fc %>% autoplot(google_2015) +
  ggtitle("Google closing stock price")
```

# Forecasting using transformations

## Forecasting with constraints

```{r}
scaled_logit <- new_transformation(
  transformation = function(x, lower=0, upper=1){
    log((x-lower)/(upper-x))
  },
  inverse = function(x, lower=0, upper=1){
    (upper-lower)*exp(x)/(1+exp(x)) + lower
  }
)
```

## Bias Adjustment

```{r}
eggs <- as_tsibble(fma::eggs)
eggs %>%
  model(RW(log(value) ~ drift())) %>%
  forecast(h=50) %>%
  autoplot(eggs, level = 80, point_forecast = lst(mean, median))
```
# Forecasting with Decomposition

```{r}
us_retail_employment <- us_employment %>%
  filter(year(Month) >= 1990, Title == "Retail Trade")
dcmp <- us_retail_employment %>%
  model(STL(Employed ~ trend(window = 7), robust=TRUE)) %>%
  components() %>%
  select(-.model)
dcmp %>%
  model(NAIVE(season_adjust)) %>%
  forecast() %>%
  autoplot(dcmp) + ylab("New orders index") +
  ggtitle("Naive forecasts of seasonally adjusted data")
```
```{r}
fit_dcmp <- us_retail_employment %>%
  model(stlf = decomposition_model(
             STL(Employed ~ trend(window = 7), robust = TRUE),
             NAIVE(season_adjust)))
fit_dcmp %>%
  forecast() %>%
  autoplot(us_retail_employment)
```
```{r}
fit_dcmp %>% gg_tsresiduals()
```

# Evaluating forecast accuracy

## Function to subset a time series

```{r}
aus_production %>% filter(quarter(Quarter) == 1)
```

```{r}
aus_production %>%
  slice(n()-19:0)
```

```{r}
aus_retail %>%
  group_by(State, Industry) %>%
  slice(1:12)
```

```{r}
gafa_stock %>%
  group_by(Symbol) %>%
  top_n(1, Close)
```
## Forecast Errors

```{r}
recent_production <- aus_production %>% filter(year(Quarter) >= 1992)
beer_train <- recent_production %>% filter(year(Quarter) <= 2007)

beer_fit <- beer_train %>%
  model(
    Mean = MEAN(Beer),
    `Naïve` = NAIVE(Beer),
    `Seasonal naïve` = SNAIVE(Beer),
    Drift = RW(Beer ~ drift())
  )

beer_fc <- beer_fit %>%
  forecast(h = 10)

beer_fc %>%
  autoplot(filter(aus_production, year(Quarter) >= 1992), level = NULL) +
  xlab("Year") + ylab("Megalitres") +
  ggtitle("Forecasts for quarterly beer production") +
  guides(colour=guide_legend(title="Forecast"))
```
```{r}
accuracy(beer_fc, recent_production)

```
```{r}
google_fit <- google_2015 %>%
  model(
    Mean = MEAN(Close),
    `Naïve` = NAIVE(Close),
    Drift = RW(Close ~ drift())
  )

google_fc <- google_fit %>%
  forecast(google_jan_2016)

google_fc %>%
  autoplot(rbind(google_2015,google_jan_2016), level = NULL) +
  xlab("Day") + ylab("Closing Price (US$)") +
  ggtitle("Google stock price (daily ending 6 Dec 13)") +
  guides(colour=guide_legend(title="Forecast"))
```

```{r}
accuracy(google_fc, google_stock)
```

# Forecast validation

```{r}
# Time series cross-validation accuracy
google_2015_tr <- google_2015 %>%
  slice(1:(n()-1)) %>%
  stretch_tsibble(.init = 3, .step = 1)
fc <- google_2015_tr %>%
  model(RW(Close ~ drift())) %>%
  forecast(h=1)

fc %>% accuracy(google_2015)

# Residual accuracy
google_2015 %>% model(RW(Close ~ drift())) %>% accuracy()
```

## Forecast Horizon Accuracy with Cross Validation

```{r}
google_2015_tr <- google_2015 %>%
  slice(1:(n()-8)) %>%
  stretch_tsibble(.init = 3, .step = 1)

fc <- google_2015_tr %>%
  model(RW(Close ~ drift())) %>%
  forecast(h=8) %>%
  group_by(.id) %>%
  mutate(h = row_number()) %>%
  ungroup()

fc %>%
  accuracy(google_2015, by = "h") %>%
  ggplot(aes(x = h, y = RMSE)) + geom_point()
```

