---
title: "Chapter 3 Time Series Decomposition"
author: "Abhishek Gupta"
date: "16/08/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggfortify)
library(fpp3)
library(fpp2)
library(tsibble)
library(feasts)
knitr::opts_chunk$set(echo = TRUE)
```

# Chapter 3 Time Series Decompostion

Learn how to extract three components of a time series: (i) Trend-Cycle, (ii) Seasonal and (iii) Remainder as well as transform or adjust the series in order to make the decomposition as simple as possible.\n

## Transformation & Adjustments

### Calendar Adjustments
### Population Adjustments

```{r}
global_economy %>%
  filter(Country == "Australia") %>%
  autoplot(GDP / Population)
```


### Inflation Adjustments


```{r}
print_retail <- aus_retail %>%
  filter(Industry == "Newspaper and book retailing") %>%
  group_by(Industry) %>%
  index_by(Year = year(Month)) %>%
  summarise(Turnover = sum(Turnover))
aus_economy <- global_economy %>%
  filter(Code == "AUS")
print_retail %>%
  left_join(aus_economy, by = "Year") %>%
  mutate(Adjusted_turnover = Turnover / CPI) %>%
  gather("Type", "Turnover", Turnover, Adjusted_turnover, factor_key = TRUE) %>%
  ggplot(aes(x = Year, y = Turnover)) +
    geom_line() +
    facet_grid(vars(Type), scales = "free_y") +
    xlab("Years") + ylab(NULL) +
    ggtitle("Turnover for the Australian print media industry")
```

### Mathematical Transformations (Box-Cox Transformation)
```{r}
lambda <- aus_production %>%
  features(Gas, features = guerrero) %>%
  pull(lambda_guerrero)
aus_production %>% autoplot(box_cox(Gas, lambda))
```

## Time Series components

```{r}
us_retail_employment <- us_employment %>%
  filter(year(Month) >= 1990, Title == "Retail Trade") %>%
  select(-Series_ID)
us_retail_employment %>%
  autoplot(Employed) +
  xlab("Year") + ylab("Persons (thousands)") +
  ggtitle("Total employment in US retail")
```
```{r}
dcmp <- us_retail_employment %>%
  model(STL(Employed))
components(dcmp)
```
```{r}
us_retail_employment %>%
  autoplot(Employed, color='gray') +
  autolayer(components(dcmp), trend, color='red') +
  xlab("Year") + ylab("Persons (thousands)") +
  ggtitle("Total employment in US retail")
```
```{r}
components(dcmp) %>% autoplot() + xlab("Year")
```

### Seasonality Adjusted Data
```{r}
us_retail_employment %>%
  autoplot(Employed, color='gray') +
  autolayer(components(dcmp), season_adjust, color='blue') +
  xlab("Year") + ylab("Persons (thousands)") +
  ggtitle("Total employment in US retail")
```

## Moving Average

```{r}
global_economy %>%
  filter(Country == "Australia") %>%
  autoplot(Exports) +
  xlab("Year") + ylab("% of GDP") +
  ggtitle("Total Australian exports")
```
```{r}
aus_exports <- global_economy %>%
  filter(Country == "Australia") %>%
  mutate(
    `5-MA` = slide_dbl(Exports, mean, .size = 5, .align = "center")
  )
aus_exports
```

```{r}
aus_exports %>%
  autoplot(Exports) +
  autolayer(aus_exports, `5-MA`, color='red') +
  xlab("Year") + ylab("Exports (% of GDP)") +
  ggtitle("Total Australian exports") +
  guides(colour=guide_legend(title="series"))
```

### Moving Average of Moving Averages

```{r}
beer <- aus_production %>%
  filter(year(Quarter) >= 1992) %>%
  select(Quarter, Beer)
beer_ma <- beer %>%
  mutate(
    `4-MA` = slide_dbl(Beer, mean, .size = 4, .align = "center-left"),
    `2x4-MA` = slide_dbl(`4-MA`, mean, .size = 2, .align = "center-right")
  )
beer_ma
```
### Trend-Cycle with seasonal data

```{r}
us_retail_employment_ma <- us_retail_employment %>%
  mutate(
    `12-MA` = slide_dbl(Employed, mean, .size = 12, .align = "cr"),
    `2x12-MA` = slide_dbl(`12-MA`, mean, .size = 2, .align = "cl")
  )
us_retail_employment_ma %>%
  autoplot(Employed, color='gray') +
  autolayer(us_retail_employment_ma, vars(`2x12-MA`), color='red') +
  xlab("Year") + ylab("Persons (thousands)") +
  ggtitle("Total employment in US retail")
```

## Classical Decomposition
### Additive & Multiplicative
```{r}
us_retail_employment %>%
  model(classical_decomposition(Employed, type = "additive")) %>%
  components() %>%
  autoplot() + xlab("Year") +
  ggtitle("Classical additive decomposition of total US retail employment")


us_retail_employment %>%
  model(classical_decomposition(Employed, type = "multiplicative")) %>%
  components() %>%
  autoplot() + xlab("Year") +
  ggtitle("Classical multiplicative decomposition of total US retail employment")
```

## X11 Additive Decomposition

```{r}
x11_dcmp <- us_retail_employment %>%
  model(x11 = feasts:::X11(Employed, type = "additive")) %>%
  components()
autoplot(x11_dcmp) + xlab("Year") +
  ggtitle("Additive X11 decomposition of US retail employment in the US")
```
```{r}
x11_dcmp %>%
  ggplot(aes(x = Month)) +
  geom_line(aes(y = Employed, colour = "Data")) +
  geom_line(aes(y = season_adjust, colour = "Seasonally Adjusted")) +
  geom_line(aes(y = trend, colour = "Trend")) +
  xlab("Year") + ylab("Persons (thousands)") +
  ggtitle("Total employment in US retail") +
  scale_colour_manual(values=c("gray","blue","red"),
             breaks=c("Data","Seasonally Adjusted","Trend"))
```

```{r}
x11_dcmp %>%
  gg_subseries(seasonal)
```

## Seasonal Extraction in ARIMA Time Series (SEATS Decomposition)

```{r}
seats_dcmp <- us_retail_employment %>%
  model(seats = feasts:::SEATS(Employed)) %>%
  components()
autoplot(seats_dcmp) + xlab("Year") +
  ggtitle("SEATS decomposition of total US retail employment")
```

## Seasonal and Trend decomposition using Loess (STL Decomposition)

```{r}
us_retail_employment %>%
  model(STL(Employed ~ trend(window=7) + season(window='periodic'),
    robust = TRUE)) %>%
  components() %>%
  autoplot()
```

