---
title: "Chapter 3 Time Series Decomposition"
author: "Abhishek Gupta"
date: "16/08/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggfortify)
library(fpp3)
library(fpp2)
library(tsibble)
knitr::opts_chunk$set(echo = TRUE)
```

# Chapter 3 Time Series Decompostion

Learn how to extract three components of a time series: (i) Trend-Cycle, (ii) Seasonal and (iii) Remainder as well as transform or adjust the series in order to make the decomposition as simple as possible.\n

## Transformation & Adjustments

### Calendar Adjustments
### Population Adjustments

```{r}
global_economy %>%
  filter(Country == "Australia") %>%
  autoplot(GDP / Population)
```


### Inflation Adjustments


```{r}
print_retail <- aus_retail %>%
  filter(Industry == "Newspaper and book retailing") %>%
  group_by(Industry) %>%
  index_by(Year = year(Month)) %>%
  summarise(Turnover = sum(Turnover))
aus_economy <- global_economy %>%
  filter(Code == "AUS")
print_retail %>%
  left_join(aus_economy, by = "Year") %>%
  mutate(Adjusted_turnover = Turnover / CPI) %>%
  gather("Type", "Turnover", Turnover, Adjusted_turnover, factor_key = TRUE) %>%
  ggplot(aes(x = Year, y = Turnover)) +
    geom_line() +
    facet_grid(vars(Type), scales = "free_y") +
    xlab("Years") + ylab(NULL) +
    ggtitle("Turnover for the Australian print media industry")
```

### Mathematical Transformations
```{r}
lambda <- aus_production %>%
  features(Gas, features = guerrero) %>%
  pull(lambda_guerrero)
aus_production %>% autoplot(box_cox(Gas, lambda))
```

## Time Series components



